Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

\subsubsection{Implementation}
We implemented our simulations by interfacing \ourframework{}
with the Alchemist Simulator~\cite{PianiniJOS2013}
through a dedicated platform module.
%
We ran experiments varying the number of participants (hence, smartphones): 100, 300, and 1000
and the \ourframework{} reconfiguration rules:
$\Uparrow$ (behaviour always in the smartphones),
$\Updownarrow^{60}_{20}$,
$\Updownarrow^{80}_{20}$,
$\Updownarrow^{60}_{40}$,
$\Updownarrow^{80}_{40}$,
$\Downarrow$ (behaviour always in the cloud).
%
All the hybrid configurations
(all except $\Uparrow$ and $\Downarrow$)
require runtime reconfiguration to be realised.
%
For each experiment, we run a total of 10 repetitions with a different random seed;
all results are averaged over them.
%
The experiment has been open sourced
and the code has been archived on Zenodo~\cite{https://doi.org/10.5281/zenodo.7948801}.
%
\begin{figure}
    \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \caption{
        A snapshot of the large-scale simulation.
        Smartphones are represented as coloured circles,
        with the color indicating their battery level
        (green when charged, red when low).
    }
    \label{fig:simulation-screenshot}
\end{figure}
%
\Cref{fig:simulation-screenshot} shows a snapshot of the simulation

>>>>

\subsubsection{Implementation}
We implemented our simulations by interfacing \ourframework{}
with the Alchemist Simulator~\cite{PianiniJOS2013}
through a dedicated platform module.
%
We ran experiments varying the number of participants (hence, smartphones): 100, 300, and 1000
and the \ourframework{} reconfiguration rules:
$\Uparrow$ (behaviour always in the smartphones),
$\Updownarrow^{60}_{20}$,
$\Updownarrow^{80}_{20}$,
$\Updownarrow^{60}_{40}$,
$\Updownarrow^{80}_{40}$,
$\Downarrow$ (behaviour always in the cloud).
%
All the hybrid configurations
(every configuration except $\Uparrow$ and $\Downarrow$)
require runtime reconfiguration.
%
We run 10 repetitions or each experiment with a different random seed;
all results are averaged over them.
%
The experiment has been open sourced
and the code has been archived on Zenodo~\cite{https://doi.org/10.5281/zenodo.7948801}.
%
\begin{figure}
    \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \caption{
        A snapshot of the large-scale simulation.
        Smartphones are represented as coloured circles,
        with the color indicating their battery level
        (green when charged, red when low).
    }
    \label{fig:simulation-screenshot}
\end{figure}
%
\Cref{fig:simulation-screenshot} shows a snapshot of the simulation
